Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-19 SDSS-2023/testing-charts-accuracy.qmd
starting to pull in content from the analysis file.

Answer 2 is the correct answer for both charts.
Both charts are shown at the same size, i.e. in both cases the difference in size between the bars is exactly the same, the vertical distance between the bars is the exact same amount.
This leaves the vertical positioning of the bars as the only difference between the charts.
Any differences in observed accuracy can therefore be attributed to this difference in presentation.

@@

Let's talk about the stacked bar flippy setup here

@@

## Study design - survey population

@@

# Notes on Analysis

I need a better name for this section...

Paragraph on applying survey weights

-   All calculations in this paper are done in R [@RLanguage] using the `survey` package [@lumleyAnalysisComplexSurvey2004] version 4.0 [@survey] based on @lumleyComplexSurveysGuide2010.

Paragraph on combining samples across rounds

-   Pull from analysis doc

-   When combining responses from multiple rounds, we make weighting adjustments to ensure that weights in each sample are properly calibrated to the population total across both rounds so each round is correctly represented in the resulting model [@omuircheartaighCombiningSamplesVs2002].
    **NEED ED REVIEW OF THIS LANGUAGE.** This adjustment is completed as follows: \[insert Heike text from analysis doc here\].

@@

## Respondents

@@

-   raw sample size and effective sample size

@@

    -   Accuracy and responses

    -   Differences in accuracy across demographic groups

@@

```{r accuracy,   warning=FALSE}
#| fig-cap: "On the left (a), a stacked barchart shows the number of respondents with correct (green) and incorrect (grey) responses to the two comparison questions. When tiles are aligned along the same axis, more than twice the number of responses is accurate. The shaded area along the top of the green tiles corresponds to  95\\% confidence intervals around (marginal) correct responses. On the right (b), a parallel coordinate plot shows all combinations of responses. There's a huge asymmetry in the number of responses, where participants answered only one of the questions correctly. A lot more responses are correct when comparing aligned tiles than unaligned tiles."
#| label: fig-alignment
#| out-width: 80%
#| fig-height: 5 
#| fig-width: 10

ANALYSIS PLAN:

Models below structured as:

Response

Covariates to use in each model

STRUCTURAL VARIATION -- START HERE

Binary accuracy across structural choices

Model 1:

Alignment only, just vertical stacked bar

Using the AmeriSpeak survey tool, a total of 1902 participants were exposed to two barcharts each, as shown in \autoref{tbl-tasks-12}.

Model 2:

Alignment

Bar vs pie (comparable question for pie is A vs B)

Model 3:

Alignment

Vertical x horizontal x horizontal wide

Model 4:

Alignment

Every structure (vertical bar, horizontal bar, horizontal wide bar, facet bar, pie)

Visuals:

\% yes across each different structural condition

Facet by aligned/unaligned?

Model estimates + CIs

Ordinal response

Model 1:

Alignment only, just vertical stacked bar

Model 2:

Alignment

Bar vs pie (comparable question for pie is A vs B)

Model 3:

Alignment

Vertical x horizontal x horizontal wide

Model 4:

Alignment

Every structure (vertical bar, horizontal bar, horizontal wide bar, facet bar, pie)

Visuals:

All responses across each different structural condition

Facet by aligned/unaligned?

Model estimates + CIs

Zooming behavior (zoomed/did not zoom)

Model 1:

Device type

Alignment

Vertical x horizontal x horizontal wide

Visuals:

\% zoomed by device + alignment (already have this chart)

Model estimates + CIs

Time spent on question (in seconds)

Model 1:

Device type

Zoom

Alignment

Vertical x horizontal x horizontal wide

Model 2 (this may not be feasible for comparison depending on what level the 'TOTALTIME' is captured at):

Device type

Zoom

Alignment

Every structure (vertical bar, horizontal bar, horizontal wide bar, facet bar, pie)

Visuals:

Distribution of time spent variable

Facet by device type, zoom, structural condition, alignment?
Play around with it

Average time spent by each of the conditions

Certainty?

Same models as above, but I'm not sure how we want to do the response.
Ordinal response?
Binary (certain or very certain vs everybody else)?

AESTHETIC VARIATION -- ONLY IF TIME

Binary accuracy (correct/incorrect -- 'they are the same' is incorrect here) across structural choices

Model 1:

Dark grid vs no grid (only have for horizontal wide)

Response choice (ordinal response)

Model 1:

Dark grid vs no grid (only have for horizontal wide)

Zooming behavior (zoomed/did not zoom)

Model 1:

Device type

Dark grid vs no grid

Time spent on question (in seconds)

Model 1:

Device type

Zoom

Dark grid vs no grid

Certainty?

Same models as above, but I'm not sure how we want to do the response.
Ordinal response?
Binary (certain or very certain vs everybody else)?

>>>>

Answer 2 is the correct answer for both charts.
Both charts are shown at the same size, i.e. in both cases both the difference in size between the bars and the horizontal distance between the bars is the exact same amount.
This leaves the vertical positioning of the bars as the only difference between the charts.
Any differences in observed responses can therefore be attributed to this difference in presentation.

@@

In \autoref{fig-tasks-3} we see two structural variations on the stacked bar chart seen in Test 1: first, the Task 1 chart sized equally but rotated 90 degrees with bar lengths shown horizontally.
Second, the horizontal chart with a smaller aspect ratio so the bars appear thinner and longer.
Note that the wide version of the horizontal bars increases the pixel difference between the two marked pieces relative to the standard versions of the horizontal and vertical bars.

This test utilized a split sample approach, where 50% of participants in the sample were shown the tall horizontal bar chart and 50% were shown the wide horizontal chart.
Participants were asked to complete the same task as in Test 1; selecting the correct response among:

Again, answer 2 is the correct answer.

@@

## Study design -- participants

@@

## Study design -- survey weighting

Paragraph on how survey weights are derived?
-- **Question for Ed -- is this something AmeriSpeak can provide boilerplate language for?**

All calculations in this paper are done in R [@RLanguage], and weights are applied in analyses using the `survey` package [@lumleyAnalysisComplexSurvey2004] version 4.0 [@survey] based on @lumleyComplexSurveysGuide2010.

When combining responses that were gathered during distinct rounds of the Omnibus survey, we make weighting adjustments to ensure that weights in each sample are properly calibrated to the population total across both rounds in the resulting model. We *combine* (rather than cumulate) surveys $S_1$ and $S_2$, as described in @omuircheartaighCombiningSamplesVs2002, by 
multiplying weights in $S_1$ and $S_2$ by $\lambda$ and $1 - \lambda$ respectively.
$$
\lambda = \frac{n_1/d_1}{n_1/d_1 + n_2/d_2},
$$
where $n_1$ and $n_2$ are the nominal sample sizes and $d_1$ and $d_2$ are the design effects for the estimators. 
Here, $d_1$ and $d_2$ are estimated as 
$$
d_1 = 1 + CV(w_i \in S_1)^2 \ \ \ \text{ and } \ \ \ d_2 = 1 + CV(w_i \in S_2)^2
$$
where $CV$ is the coefficient of variation of the weights within each sample, and is estimated as in @kishSurveySampling1965 :

$$ 
CV(w \in S) = \frac{\widehat{Var(w)}}{\bar{w}^2}.
$$

Note that @omuircheartaighCombiningSamplesVs2002 estimate $\lambda$ separately for any combination of race/ethnicity by sex. We employ that strategy whenever we include demographic variables in the analysis, otherwise we will use a single adjustment for the weights.

@@

### Respondents

@@

-   raw sample size and effective sample size that we are analyzing **in each test**

@@

    -   Binary accuracy in responses

        -   Figure: binary correctness and binary ggpcp diagram
        -   Table:(?) T-test results
        -   Table: results of cell means model on certainty

    -   Ordinal accuracy in responses

        -   Figure: ordinal correctness and ordinal ggpcp diagram

        -   Table: Fitted model for ordinal response and alignment

    -   Ordinal accuracy in responses by demographics

        -   Figure: ordinal correctness by demographics, split by aligned and unaligned

        -   Table: Fitted model for ordinal response and alignment by demos

            -   Maybe this table should go in the appendix?

```{r accuracy,   warning=FALSE}
#| fig-cap: "On the left (a), a stacked barchart shows the number of respondents with correct (green) and incorrect (grey) responses to the two comparison questions. When tiles are aligned along the same axis, more than twice the number of responses is accurate. The shaded area along the top of the green tiles corresponds to  95\\% confidence intervals around (marginal) correct responses. On the right (b), a parallel coordinate plot shows all combinations of responses. There's a huge asymmetry in the number of responses where participants answered only one of the questions correctly. A lot more responses are correct when comparing aligned tiles than unaligned tiles."
#| label: fig-alignment
#| out-width: 80%
#| fig-height: 5 
#| fig-width: 10

@@
